Meaningful data sharing

### 2020-09-23 new-paper.Rmd
remove carbon sh figure for dir layout and other unused figures

Avoid using non-standard licenses, such as those custom written by the authors, as some terms can render them unusable. Once a license is chosen, a LICENSE file should be provided, containing the entire license in the top level of the directory (Figure \@ref(fig:dir-layout)). The license type should be mentioned in the README, if used.

```{r dir-layout, fig.cap = "Example directory layout and structure for sharing data. Note ..."}
# insert carbon.sh figure showing file structure layout
knitr::include_graphics("figures/carbon-dir-layout.png")
```

@@

Share code used to transform data from its raw format into analysis ready form. This should be kept in the same place as raw data (Section \@ref(fig:dir-layout)). Ideally, this transformation should involve only scripted languages (e.g, R, Python, Matlab, etc), but any non-scripted data preparation steps should be recorded in a plain text file. Authors should run the scripts in a clean environment to make sure everything runs and that the code doesn’t rely on other local artifacts.

@@

Describe how you want your data to be cited in a CITATION file. Citation is important for provenance, and credit. Citing data clarifies the data version used (provenance), and provides authors a citation (credit). To ensure these are provided, data needs to have an accession number, such as a Digital Object Identifier (DOI). A DOI is a permanent, unique identifier for a digital object such as a paper, poster, or software. Access numbers are a prerequisite for citation - if they are unavailable, a citation will be meaningless, as it cannot be tracked by any means. A file named CITATION should be placed in the directory at the top level (Figure \@ref(fig:dir-layout)). It should contain an accession number, and could be in `.bibtex` format. Avenues that provide DOIs are discussed in Section \@ref(avenues).

>>>>

Avoid using non-standard licenses, such as those custom written by the authors, as some terms can render them unusable. Once a license is chosen, a LICENSE file should be provided, containing the entire license in the top level of the directory. The license type should be mentioned in the README, if used.

@@

Share code used to transform data from its raw format into analysis ready form. This should be kept in the same place as raw data. Ideally, this transformation should involve only scripted languages (e.g, R, Python, Matlab, etc), but any non-scripted data preparation steps should be recorded in a plain text file. Authors should run the scripts in a clean environment to make sure everything runs and that the code doesn’t rely on other local artifacts.

@@

Describe how you want your data to be cited in a CITATION file. Citation is important for provenance, and credit. Citing data clarifies the data version used (provenance), and provides authors a citation (credit). To ensure these are provided, data needs to have an accession number, such as a Digital Object Identifier (DOI). A DOI is a permanent, unique identifier for a digital object such as a paper, poster, or software. Access numbers are a prerequisite for citation - if they are unavailable, a citation will be meaningless, as it cannot be tracked by any means. A file named CITATION should be placed in the directory at the top level. It should contain an accession number, and could be in `.bibtex` format. Avenues that provide DOIs are discussed in Section \@ref(avenues).
